Search for Spatially Extended \fermi-LAT Sources Using Two Years of Data

### 2012-02-16 presentations/extended_source_search/lande_ext_src_search_fermi_lunch/lande_ext_src_search_fermi_lunch.tex
improve
update

@@

\begin{frame}{Section 7: extended sources in 2FGL}
  \begin{columns}
    \column{.6\textwidth}
    \includegraphics[scale=0.4]{plots/table_reanalysis.pdf}
    \column{.4\textwidth}
    \begin{itemize}
      \item Test 12 extended 2FGL sources for extension
      \item Systematic reanalysis using 2 years of data.
      \item Assume uniform disk
      \item Extended sources are extended!
    \end{itemize}
  \end{columns}
\end{frame}

@@

@@

\begin{frame}{Section 10: New extended Sources}
  \begin{columns}
    \column{.65\textwidth}
    \includegraphics[scale=0.30]{plots/new_extended.png}
    \column{.35\textwidth}
    \begin{itemize}
      \item 6 new extended sources
      \item + RX J1713-3946 \& Vela Jr (not extended in 2FGL)
      \item + 1 source in Ophiuchus region $\rightarrow$ diffuse emission
    \end{itemize}
  \end{columns}
\end{frame}

@@

@@

>>>>

\begin{frame}{Table 2: Detection Threshold (cont)}
  \includegraphics[scale=0.5]{plots/threshold_table.pdf}
\end{frame}

@@

\begin{frame}{Table 3: extended sources in 2FGL}
  \begin{columns}
    \column{.6\textwidth}
    \includegraphics[scale=0.4]{plots/table_reanalysis.pdf}
    \column{.4\textwidth}
    \begin{itemize}
      \item Test 12 extended 2FGL sources for extension
      \item Systematic reanalysis using 2 years of data.
      \item Assume uniform disk
      \item Extended sources are extended!
    \end{itemize}
  \end{columns}
\end{frame}

@@

\begin{frame}{Table 4: New extended Sources}
  \begin{columns}
    \column{.65\textwidth}
    \includegraphics[scale=0.30]{plots/new_extended.pdf}
    \column{.35\textwidth}
    \begin{itemize}
      \item 6 new extended sources
      \item + RX J1713-3946 \& Vela Jr (not extended in 2FGL)
      \item + 1 source in Ophiuchus region $\rightarrow$ diffuse emission
    \end{itemize}
  \end{columns}
\end{frame}

@@

\begin{frame}{Table 5: Dual Localization, alternative PSF, alternative Diffuse}
  \includegraphics[scale=0.40]{plots/alt_diff.pdf}
\end{frame}

@@

\begin{frame}{Fig. 14: SED of SNRs}
  \includegraphics[scale=0.5]{plots/snr_seds_color.pdf}
\end{frame}

@@

\begin{frame}{Fig. 18: SED of HESS Sources}
  \includegraphics[scale=0.5]{plots/hess_seds_color.pdf}
\end{frame}

\begin{frame}{Fig. 20: SED of RX J1713.7$-$3946}
  \includegraphics[scale=0.5]{plots/source_RX_J1713_7-3946_color.pdf}
\end{frame}
